P4IRS: An Intermediate Representation and Compiler for Parallel and Performance-Portable Particle Simulations

### 2025-04-27 sage_latex_template/manuscript.tex
Add table for DEM cases
Signed-off-by: Rafael Ravedutti <rafael.r.ravedutti@fau.de>

\begin{table*}[htb]
    \centering
    \begin{tabular}{c|c|c|c|c}
%        \hline
        Variant & pairs-fn & mdbench-fn & pairs-hn & mdbench-hn \\
        \hline
        Ice Lake & 0.962 & 1.019 & 1.662 & 1.595 \\
        Milan & 0.908 & 0.883 & 1.354 & 1.367 \\
        A40  & 26.452 & 27.025 & 29.688 & --- \\
        A100 & 75.113 & 87.381 & 87.968 & --- \\
%        \hline
    \end{tabular}
    \caption{\RMchange{Summary of performance results (in million particle updates per second) for each P4IRS and MD-Bench simulation runs on a single core of Ice Lake and Milan CPUs, and one A40 and A100 GPUs.}}
    \label{tab:md_particle_updates_per_second_cpu}
\end{table*}

>>>>

\begin{table*}[htb]
    \centering
    \begin{tabular}{c|c|c|c|c}
%        \hline
        Variant & pairs-fn & mdbench-fn & pairs-hn & mdbench-hn \\
        \hline
        Ice Lake & 0.962 & 1.019 & 1.662 & 1.595 \\
        Milan & 0.908 & 0.883 & 1.354 & 1.367 \\
        A40  & 26.452 & 27.025 & 29.688 & --- \\
        A100 & 75.113 & 87.381 & 87.968 & --- \\
%        \hline
    \end{tabular}
    \caption{\RMchange{Summary of performance results (in million particle updates per second) for each P4IRS and MD-Bench simulation runs of the MD benchmark on a single core of Ice Lake and Milan CPUs, and one A40 and A100 GPUs.}}
    \label{tab:md_particle_updates_per_second_md}
\end{table*}

\begin{table*}[htb]
    \centering
    \begin{tabular}{c|c|c|c|c|c|c|c}
        Variant & pairs-fn & pairs-fn-nb & pairs-fn-2r & pairs-fn-nb-2r & pairs-fn-mk & pairs-fn-nb-mk & mesapd \\
        \hline
        Ice Lake & 76.573 & 48.549 & 164.202 & 101.062 & --- & --- & 47.304 \\
        Milan & 113.229 & 68.008 & 225.374 & 134.969 & --- & --- & 64.347 \\
        A40 & 68.866 & 83.06 & --- & --- & 63.835 & 79.828 & --- \\
        A100 & 210.41 & 235.753 & --- & --- & 209.969 & 251.292 & --- \\
    \end{tabular}
    \caption{\RMchange{Summary of performance results (in million particle updates per second) for each P4IRS and MESA-PD simulation runs of the DEM benchmark on a single core of Ice Lake and Milan CPUs, and one A40 and A100 GPUs.}}
    \label{tab:md_particle_updates_per_second_dem}
\end{table*}
